---
title: 'Data Science Project Guide: Netflix'
author: "TechAcademy e.V."
date: "Wintersemester 2022/23"
geometry: top=0.5in, bottom=1.5in, left=1in, right=1in, a4paper
fontsize: 11pt
fontfamily: mathpazo
bibliography:
- book.bib
- packages.bib
biblio-style: apalike
link-citations: yes
urlcolor: blue
description: Everything you need to know for your successful TechAcademy Data Science
  Project
site: bookdown::bookdown_site
editor_options: 
  markdown: 
    wrap: sentence
---

```{r eval=FALSE, include=FALSE}
install.packages("bookdown")
install.packages("tinytex")
library(tinytex)
# or the development version
# devtools::install_github("rstudio/bookdown")
```

```{r global_options, include=FALSE}
# knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
#                       echo=FALSE, warning=FALSE, message=FALSE)
knitr::opts_chunk$set(fig.width=12, fig.height=8,
                      warning=FALSE, message=FALSE, comment=">")
#echo=FALSE,
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

\clearpage

```{=tex}
\addtolength{\headheight}{17.82275pt}
\rhead{\includegraphics[height=0.5cm]{plot/TA_logo.png}}
```
```{=tex}
\fancyfoot{}
\fancyfoot[R]{\thepage}
\addtolength{\headheight}{17.82275pt}
```
\fancyfoot[L]{Data Science Project Guide | Honey and Bees | \copyright\ 2022, TechAcademy e.V.}

```{=tex}
\renewcommand{\headrulewidth}{0.25pt}
\renewcommand{\footrulewidth}{0.25pt}
```
```{=tex}
\tableofcontents
\clearpage
```


# Welcome!
Let us start with an overview of what is waiting for you in the next weeks and in this project guide!
If you are a beginner,In the first few chapters you will be introduced to the basics of the `R` and `Python` tracks respectively and you will find helpful explanations to questions you might have in the beginning of your coding journey. There will be a quick introduction to the Data Science track so that you can get started with the project quickly. So let’s get started with the basics!
You will work on your project in small groups of fellow students. This not only helps you get the project done faster, it also helps make your results even better. Our experience shows: Contrasting university backgrounds and different opinions and ideas will produce the best results. Besides, it is of course more fun to work on a project together than to code alone! The groups can consist of a maximum of four members and you can choose your teammates independently. We explicitly encourage you to collaborate with students from different departments. 
When submitting your final project, it is important to note: for a certificate, each person must submit the project individually. However, this can be identical within your group. You can get more information at our “Introduction to Coding” Workshop  on November 9, 2022 or at our first Coding Meetup on November 23, 2022.
This Netflix case study and the associated project guide was developed and written entirely from scratch by TechAcademy’s Data Science team. Jessica Weigel and Isabel Schnorr developed the project in `R`, while Lea Karoza, Moritz Schwerdt and Rocky Auer developed it in `Python`.
