---
title: "Advanced Netflix RS"
author: "Jessie"
date: "10/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r installing packages, include=FALSE}
install.packages("tidyverse", repos = "http://cran.us.r-project.org")
install.packages("ggplot2", repos = "http://cran.us.r-project.org")
install.packages("ggthemes", repos = "http://cran.us.r-project.org")
install.packages("leaflet", repos = "http://cran.us.r-project.org")
install.packages("lubridate", repos = "http://cran.us.r-project.org")
install.packages("plotly", repos = "http://cran.us.r-project.org")
install.packages("readr", repos = "http://cran.us.r-project.org")
install.packages("tidyr", repos = "http://cran.us.r-project.org")
install.packages("tm", repos = "http://cran.us.r-project.org")
install.packages("SnowballC", repos = "http://cran.us.r-project.org")
install.packages("lsa", repos = "http://cran.us.r-project.org")
```

```{r loading packages, include=FALSE}
library(readr)
library(tidyverse)
library(lubridate)
library(tidyr)
library(ggplot2)
library(ggthemes)
library(leaflet)
library(plotly)
library(tm)
library(SnowballC)
library(lsa)
```

# First steps
```{r}
netflix_data <- read.csv("~/Desktop/Tech Academy/Netflix Project/netflix_titles.csv")
```

Remove unrelevant columns:
```{r}
netflix_clean <- netflix_data %>%
  select(-c(country,date_added,release_year,rating,duration))
```


# Second steps: Vorbereitung for recommendation system --> Description, Genre & Actors
Weiters Vorgehen bzgl bag of words:
https://thibaut-deveraux.medium.com/how-to-create-a-bag-of-words-embedding-in-r-e609095ebf53

## Preperation for description

Creating corpus
```{r}
netflix_descr_corpus <- VCorpus(VectorSource(netflix_clean$description))
```

Document term matrix for words
```{r}
control_list_words = list(
  tokenize = words,
  language="en",
  bounds = list(global = c(100, Inf)),
  tolower = TRUE,
  removePunctuation = TRUE,
  stopwords = TRUE,
  stemming = TRUE
)
```

Making a document-term matrix
```{r}
netflix_descr <- DocumentTermMatrix(netflix_descr_corpus, control = control_list_words)
netflix_descr <- as.matrix(netflix_descr)
```

### Cosine Similarity of each movie

Titles have to be represented as columns so I need to transpose the matrix
```{r}
# Convert into numeric
netflix_descr <- matrix(as.numeric(netflix_descr),ncol = ncol(netflix_descr))
# Transpose Matrix
netflix_descr <- t(netflix_descr)
# Column names titles
colnames(netflix_descr) <- netflix_clean$title
```

Calculate cosine similarity (not from scratch)
```{r}
cos_descr <- cosine(netflix_descr)
```

Define dataframe so that I can use dplyr and replace all NAs to 0
```{r}
descr_dataframe <- as.data.frame(cos_descr)
descr_dataframe[is.na(descr_dataframe)] <- 0
```


## Prep genre

get rid off space and delete ,
```{r}
netflix_genre <- netflix_clean %>%
  select(c(title,listed_in))

netflix_genre$listed_in <- gsub(" ","",netflix_genre$listed_in)
netflix_genre$listed_in <- gsub(","," ",netflix_genre$listed_in)

```

Create corpus
```{r}
netflix_genre_corpus <- VCorpus(VectorSource(netflix_genre$listed_in))
```

Making a document-term matrix
```{r}
netflix_genre <- DocumentTermMatrix(netflix_genre_corpus, control = control_list_words)
netflix_genre <- as.matrix(netflix_genre)
```

### Cosine Similarity of each movie

```{r}
# Convert into numeric
netflix_genre <- matrix(as.numeric(netflix_genre),ncol = ncol(netflix_genre))
# Transpose Matrix
netflix_genre <- t(netflix_genre)
# Column names titles
colnames(netflix_genre) <- netflix_clean$title
```

```{r}
cos_genre <- cosine(netflix_genre)
```

```{r}
genre_dataframe <- as.data.frame(cos_genre)
genre_dataframe[is.na(genre_dataframe)] <- 0
```

## Prep actor

get rid off space and delete ,
```{r}
netflix_actor <- netflix_clean %>%
  select(c(title,cast))

netflix_actor$cast <- gsub(" ","",netflix_actor$cast)
netflix_actor$cast <- gsub(","," ",netflix_actor$cast)
```

Create corpus
```{r}
netflix_actor_corpus <- VCorpus(VectorSource(netflix_actor$cast))
```

We need a new list for actors since they usually don't include normal english words, and we don't need to delete stopwords or create stemmings
```{r}
control_list_words_people = list(
  tokenize = words,
  #language="en",
  bounds = list(global = c(10, Inf)),
  tolower = TRUE,
  removePunctuation = TRUE
  #stopwords = TRUE,
  #stemming = TRUE
)
```

Making a document-term matrix
```{r}
netflix_actor <- DocumentTermMatrix(netflix_actor_corpus, control = control_list_words_people)
netflix_actor <- as.matrix(netflix_actor)
```

### Cosine Similarity of each movie

```{r}
# Convert into numeric
netflix_actor <- matrix(as.numeric(netflix_actor),ncol = ncol(netflix_actor))
# Transpose Matrix
netflix_actor <- t(netflix_actor)
# Column names titles
colnames(netflix_actor) <- netflix_clean$title
```

```{r}
cos_actor <- cosine(netflix_actor)
```

```{r}
actor_dataframe <- as.data.frame(cos_actor)
actor_dataframe[is.na(actor_dataframe)] <- 0
```

# Loop for recommendation

This step already happens in the beginner track, so you can ignore this part of reading Tobis file with watch history & preparing it for the loop.
The only important thing is, that you need to sort Tobis viewing history chronological so that the loop can start with the last seen movie.
```{r}
tobi_data <- read_csv("~/Desktop/Tech Academy/Netflix Project/ViewingActivity.csv",show_col_types = FALSE)
tobi_data <- tobi_data %>%
  mutate(duration_min=as.numeric(as.duration(hms(Duration))/60)) %>%
  mutate(date=as.Date(`Start Time`),.after=`Start Time`) %>%
  mutate_if(is.numeric,round,0) %>%
  filter(duration_min>0,!`Supplemental Video Type`%in% c("TRAILER")) %>%
  select(-c(Attributes,`Supplemental Video Type`,`Device Type`,Bookmark,`Latest Bookmark`,Country)) %>%
  rename(profile_name=`Profile Name`, start_time=`Start Time`) %>%
  mutate(title_duplicate=Title) %>%
  separate(col = title_duplicate, into = c("title", "season", "episode"), sep = ': ')

tobi_data$category <- "TV Show"
tobi_data$category[is.na(netflix_data$episode)==TRUE] <- "Movie"

tobi_data <- tobi_data %>%
  mutate(title_new = ifelse(category=="Movie", Title, title)) %>%
  filter(profile_name == "Tobi") %>%
  arrange(desc(date)) %>%
  select(c(title_new)) 
  
tobi_data <- unique(tobi_data)
```

```{r}
i <- 0
j <- 1

for (j in 1:nrow(tobi_data)) {
  movie <- tobi_data[j,1]
  if (movie %in% netflix_clean$title) {
    
    movie <- as.character(movie)
    test_genre <- genre_dataframe %>%
      select(movie) %>%
      rename(genre = movie)
    
    test_actor <- actor_dataframe %>%
      select(movie) %>%
      rename(cast = movie)
    
    test_descr <- descr_dataframe %>%
      select(movie) %>%
      rename(descr = movie) %>%
      mutate(genre = test_genre$genre, cast = test_actor$cast) %>%
      mutate(final = 2/6*descr + 3/6*genre + 1/6*cast) %>%
      arrange(desc(final))
    # Jeder soll seine eigene Gewichtung festlegen
    
    print(paste("Top 10 recommendations for",movie))
    print(row.names(test_descr[2:11,]),right = FALSE)
    
    i <- i+1
    
    if (i > 5) {
      break
    }
  }
  j <- j+1
}
```
